Ceph Parallel File System Evaluation Report

### 2013-08-16 ceph-eval.tex
patch with Doug's input

NCCS contracted Inktank, the major developer behind the open-sourced parallel
file system, Ceph, for a deep-dive study. It covers a wide range of technical
topics: from system setup, deployment, administration to \hl{internal mechanism}. In
comparison to other parallel file systems, Ceph has a number of distinctive
features:

\begin{itemize}
  \item Ceph has an intelligent and powerful data placement mechanism, known as
  CRUSH. The CRUSH algorithm allows a client to pre-calculate the layout
  info, while taking into consideration failure domains and hierarchical storage tiers.

@@

\item Ceph's design assumes that the system is composed of
unreliable components; fault-detection and fault-tolerance (e.g., replication) are
the norm rather than the exception. This is in line with the expectation of
exascale computing.

@@

\item Most of the Ceph processes reside in user-space. Generally speaking, it makes the
system easier to debug and maintain. The client-side support has long been
integrated into Linux mainline kernel, which make the deployment and out-of-box
experience easier.

@@

As part of this effort, we set up a dedicated testbed within NCCS for Ceph
system evaluation. The goal is to investigate the feasibility of using the Ceph system as
a potential candidate for our next-generation HPC storage solution.
This report presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph is such a moving target that its
code base is changing rapidly. In between releases, we often experienced different
outcomes. We will try to make clear when such changes happened in the report.

@@

We used Data Direct Network's (DDN) SFA10K as the storage backend during this evaluation. It consists of
200 SAS drives and 280 SATA drives, driven by four hosts. Each host has two InfiniBand (IB) QDR
connections to the storage backend. We configured and used four Mellanox IB cards as the
primary connections, which by calculation can saturate the maximum theoretical
throughput (11-12 GB/s). The connection diagram is illustrated as the
following:

@@

The hosts ran Redhat 6.3 with 3.5.1 kernel (rhl-ceph image), Glibc 2.12
with syncfs support, locally patched. We used the Ceph 0.55 release in the
initial tests, then upgraded to 0.64 and then to 0.67RC for second round of tests. For a
complete a list of hosts that are running ceph images, one can execute:

@@

\subsection*{Block I/O}
We first establish the baseline performance by measuring block I/O performance.
At the block level, with each LUN configured with RAID6 8+2, we have the following
results:

@@

Single host refers to one of four tick-oss nodes, which drives the entire SSU.
Overall, the entire SSU performance can perform at 11 GB/s, comparing to
theoretical maximum of 12 GB/s.

@@

Note, Ceph uses the BSD Sockets interface in the \texttt{SOCK\_STREAM} mode (i.e., TCP).
Because our testbed has IB, we used IP over IB (IPoIB) for networking\footnote{Inktank is 
investigating using rsockets to improve performance when using an IB fabric}.
A pair of hosts connected by IB QDR using IPoIB can transfer data at 2.7 GB/s if the
hosts are tuned per recommendations from Mellanox. With all four hosts (OSD servers), we would expect
the aggregate throughput to be in the neighborhood of 10 GB/s.

@@

Base upon past experience and further experimentation, we started out on the
following set of tuning parameters:

@@

%% Are the read and write graphs wrong or should the second sentence below be about write
%% instead of read?
The read and write results are summarized in Figures~\ref{fig:xfs-read}
and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
indicates that XFS can get to the peak write performance with five SATA LUNs,
then there is a bit of degradation from there. Changes to
the queue depth do not seem to make any obvious difference on the performance.

@@

RADOS is the Ceph object store, a foundational component for CephFS file
system. There are three types of scaling tests we are interested at RADOS layer:

@@

Our system setup poses some limitation on the scalability tests we want to
perform. In particular, we currently have four OSS servers, eight clients, and eleven OSD servers
per client. The scaling tests will be within these constraints.

We use the open-source tool RADOS bench, developed by Inktank, to perform our
initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
writes out objects to the underlying object storage as fast as possible, and
then later reads those objects in the same order as they were written.

We have observed that using two or more client processes and many concurrent
operations are important when performing these tests.  We tested eight client processes 
with 32 concurrent 4 MB objects in flight each. We created a pool for
each RADOS bench process to ensure that object reads come from independent pools
(RADOS bench is not smart enough to ensure that objects are not read by multiple
processes and thus possibly cached).  A sync and flush is performed on every
node before every test to ensure no data or metadata is in cache.  All tests
were run with replication set to one.  Only XFS was present
and usable for the underlying OSDs, so BTRFS and EXT4 file systems were not
tested at this time.

@@

In the following test, a single Ceph host drives $n$ number of OSDs, where $n$
increases from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
We ran the test against a single client with four concurrent processes. In this test
case, we observe that the OSS exhibits near linear scalability up to nine
OSDs, and is still trending upwards at eleven OSDs. This suggests that we have not reached the
saturation point yet. Additional testing would require provisioning more OSDs on the SFA10K backend.

@@

In this test, we exercise OSS number from one to four, driven by four clients with four
concurrent process for each client. Each addition of OSS adds eleven more OSDs into
play. We observe that Ceph exhibits linear scaling property with regard to
number of servers as well, at least in the given set of servers. However, the peak
performance we are seeing is about the half of what are expecting from SFA10K.
For the write, the reason behind it is attributed to the way Ceph perform
journaling: Ceph does not support the meta-data only journaling, therefore every
write is equivalent of a double-write: once to the data device, once to the
journaling device. It effectively cut the system bandwidth in half. That said,
it does not explain the read performance - though it is better than write, but is
still far from the theoretical maximum.

@@

We use synthetic IOR benchmark suite for file system level test. The particular
parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB
physical memory, the block size is set so as to mitigate the cache effect. In
addition, the test harness program will issue the following command at the
beginning of each test:

@@

Our first round of test was less than ideal as we encountered various issue. For
the sake of completeness, we still first summarized the results, then discuss
the further tuning efforts and improvements.

The full permutation of IOR parameters are not explored due to IO errors we ran
into. We were, however, able to record results in two extreme case as far as
transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
(4) and same block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

@@

\begin{itemize}
  \item The small read performance is almost an anomaly - we need to
  investigate why it is so low compare to write.
  \item The large read performance is almost half of the write performance,
  which is the opposite of RADOS level. 
  \item The write performance is cut in half compare to what we can obtain from
  RADOS benchmark. And number of clients reaches 8, there is a significant
  performance drop as well. 
\end{itemize}

@@

As a result of this testing, performance was again improved slightly by
increasing the size of various Ceph buffers and queues, enabling aio journals,
and increasing the number of OSD op threads.

\subsection{Disable Cache Mirroring on DDN}

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  A significant amount of time was spent
investigating this phenomena. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The 2nd RAID processor on each DDN controller would max out when
3 or more LUNs were written concurrently. It turns out the root of the problem
is attributed to a regression on DDN firmware update - in particular, the cache
mirroring is not behaving as it should be.

@@

With cache mirroring disabled write performance when using all four servers
improved dramatically, as illustrated in
Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS for example, we hit over
5.5 GB/s from the clients.  When accounting for journal writes, that is over
11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
Unfortunately, read performance did not scale as well.

@@

During these tests, a trend that previously had been seen became more apparent.
During reads, there were periods of high performance followed by periods of low
performance or outright stalls that could last for up to 20 seconds at a time. 
After several hours of diagnostics, Inktank observed that outstanding operations
on the clients were not being shown as outstanding on the OSDs.  This appeared
to be very similar to a problem Jim Schutt at Sandia National labs encountered
with TCP autotuning in the Linux Kernel.
\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}.
TCP auto tuning enables TCP window scaling by default and automatically adjust
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this will make a notable improvement
on Ceph read performance, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

@@

We now repeated previous RADOS scaling test with these improvements in place.
The first test was done on a single node with RADOS bench to see how close the
underlying object store could get to the node hardware limitations as the number
of OSDs/LUNs used on the node increase. Note all the tests performed are against
XFS formatted storage.

@@

We also repeated tests looking at RADOS Bench performance as the
number of OSD server nodes increases. The result is summarized in
Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
scales nearly linearly for both reads and writes.

@@

The initial stability issues we encountered are fixed by moving Ceph version
from 0.48/0.55 to 0.64, latest stable at the time. Now IOR test can proceed to
finish even during long runs. It is another sign of showing how much Ceph
development is in flux.

Another fix comes the way we create the pool: the default data pool being used
by previous CephFS cluster are set to 2x replication, which can potentially
halve the write performance. Even with these changes in place, Inktank still
reproduced the less-than-ideal write performance and very poor read
performance as observed by ORNL.  Further, by increasing the number of IOR
processes per client node, read performance actually degraded further
indicating some kind of contention either on the clients or on the OSD
servers.

@@

ORNL at this point was able to both make more client nodes available and also
install a profiling tool called \verb!perf! that is extremely useful for
profiling both kernel and user space code.  Profiling with \verb!perf! showed
high CPU utilization on the client due to crc32c processing in the Ceph kernel
client.  Luckily crc32 checksums can be disabled by changing the CephFS mount
options:

@@

We observed that IOR write throughput increased dramatically and is now very
close to the throughput we were able to achieve with RADOS Bench, but reads
continued to be slow, and continued to inversely scale with the number of client
processes.  Please note that since these tests were performed, Inktank has
implemented SSE4 based CRC32 code for Intel CPUs.  While any kernel based CRC32
processing should have already been using SSE4 instructions on Intel CPUs, this
will allow any user land Ceph processes to process CRC32 checksums with
significantly less overhead.

@@

ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
RADOS bench test to verify that there was no degradation vs previous tests.  The
results were extremely positive.

@@

With the kernel changes writes performance improved slightly, while read
performance improved dramatically.  In addition to the kernel change, Sage Weil
suggested increasing the amount of read ahead being performed by the CephFS
kernel client:

@@

By installing a new kernel, increasing read ahead, and increasing the number of
client IOR processes, we were able to achieve a very satisfactory result on this
test run.

@@

As before, we ran IOR scaling test with two cases: transfer size 4 KB and 4 MB.
These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
seeing a much improved picture of read and write performance, very much in
line with RADOS bench performance.

@@

We observe that a couple of places where the average write throughput is quite a
bit lower than the max.  This behavior was observed during other tests as well,
indicating that we may have periods of time where write throughput is
temporarily degrading.  Despite these issues, performance general seems to be
improving as the number of clients increases.  Writes seem to be topping out at
around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
saw with RADOS Bench.

@@

  \item Ceph is built on the assumption that the underlying hardware components
  is unreliable, with little or no redundancy and failure detection capability.
  This is not the case in this leadership computing facilities. We have disabled
  replication for pools, but this will take a toll somewhere in the processing
  and we do not know if this is significant.

  \item Ceph do \textbf{metadata + data} journaling, which is fine for host
  system that has locally attached disk. However, this presents a problem in DDN
  SFA10-like hardware, where the backend LUNs are exposed as block device
  through SRP over IB. The journaling write would requires double bandwidth
  compare to Lustre-like metadata only journaling mechanism. For Ceph to anything
  viable in this facility, there has to be a solution for this.

  \item Ceph is observed to have consist results and linear scalability at the
  RADOS level. However, it broke down at the file system level with synthetic
  benchmark suite such as IOR. We have experience large performance swings
  during different runs, very low read performance when transfer size is small,
  and IO errors tend to happen when system is under stress (more clients and
  large transfer size). These are not particularly reproducible results, but it
  suggests the level of maturity still have a long way to go.

@@

This crush map is just an example of full OSD mapping. As we create and
re-create different testbed with different OSD configurations, the map will
change accordingly.

>>>>

NCCS contracted Inktank, the major developer behind the open-source parallel
file system, Ceph, for a deep-dive study. It covers a wide range of technical
topics from system setup, deployment, administration to \hl{internal mechanisms}. In
comparison to other parallel file systems, Ceph has a number of distinctive
features:

\begin{itemize}
  \item Ceph has an intelligent and powerful data placement mechanism, known as
  CRUSH. The CRUSH algorithm allows a client to pre-calculate layout
  information while taking into consideration failure domains and hierarchical storage tiers.

@@

\item Ceph's design assumes that the system is composed of
unreliable components; fault-detection and fault-tolerance (e.g., replication) are
the norm rather than the exception. This is in line with the expectations of
exascale computing.

@@

\item Most of the Ceph processes reside in user-space. Generally speaking, this makes the
system easier to debug and maintain. The client-side support has long been
integrated into Linux mainline kernel, which make the deployment and out-of-box
experience easier.

@@

As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
system evaluation. The goal is to investigate the feasibility of using the Ceph system as
a candidate for our next-generation HPC storage solution.
This report presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph is such a moving target that its
code base is changing rapidly. In between releases, we often experienced different
outcomes. We will try to make clear in the report when such changes occurred.

@@

We used Data Direct Networks' (DDN) SFA10K as the storage backend during this evaluation. It consists of
200 SAS drives and 280 SATA drives driven by four hosts. Each host has two InfiniBand (IB) QDR
connections to the storage backend. We configured and used four Mellanox IB cards as the
primary connections, which by calculation can saturate the controller's maximum theoretical
throughput (11-12 GB/s). The connection diagram is illustrated below:`

@@

The hosts ran Redhat 6.3 with kernel version 3.5.1 (rhl-ceph image), Glibc 2.12
with syncfs support, locally patched. We used the Ceph 0.55 release in the
initial tests, then upgraded to 0.64 and then to 0.67RC for second round of tests. For a
complete a list of hosts that are running ceph images, one can execute:

@@

\subsection*{Block I/O}
We first establish baseline performance by measuring block I/O performance.
At the block level, with each LUN configured with RAID6 8+2, we have the following
results:

@@

Single host refers to one of four tick-oss nodes, which drives the entire system.
Overall, the entire system can perform at 11 GB/s, compared to its
theoretical maximum of 12 GB/s.

@@

Note that Ceph uses the BSD Sockets interface in \texttt{SOCK\_STREAM} mode (i.e., TCP).
Because our testbed has IB, we used IP over IB (IPoIB) for networking\footnote{Inktank is 
investigating using rsockets to improve performance when using an IB fabric}.
A pair of hosts connected by IB QDR using IPoIB can transfer data at 2.7 GB/s if the
hosts are tuned per recommendations from Mellanox. With all four hosts (OSD servers), we would expect
the aggregate throughput to be in the neighborhood of 10 GB/s.

@@

Base upon past experience and further experimentation, we started out with the
following set of tuning parameters:

@@

%% Are the read and write graphs wrong or should the second sentence below be about write
%% instead of read?
The read and write results are summarized in Figures~\ref{fig:xfs-read}
and~\ref{fig:xfs-write}, respectively. These show scaling behavior over the number of devices, which
indicates that XFS can get to the peak write performance with five SATA LUNs,
then there is a bit of degradation from there. Changes to
the queue depth do not seem to make any obvious difference in the performance.

@@

RADOS is the Ceph object store, a foundational component for CephFS file
system. There are three types of scaling tests we are interested at the RADOS layer:

@@

Our system setup poses some limitations on the scalability tests we want to
perform. In particular, we currently have four OSS servers, eight clients, and eleven OSD servers
per client. The scaling tests will be within these constraints.

We use the open-source tool RADOS Bench, developed by Inktank, to perform our
initial performance analysis of the underlying RADOS layer.  RADOS Bench simply
writes out objects to the underlying object storage as fast as possible, and
then later reads those objects in the same order as they were written.

We have observed that using two or more client processes and many concurrent
operations are important when performing these tests.  We tested eight client processes 
with 32 concurrent 4 MB objects in flight each. We created a pool for
each RADOS Bench process to ensure that object reads come from independent pools
(RADOS Bench is not smart enough to ensure that objects are not read by multiple
processes and thus possibly cached).  A sync and flush is performed on every
node before every test to ensure no data or metadata is in cache.  All tests
were run with replication set to one.  Only XFS was present
and usable for the underlying OSDs, so BTRFS and EXT4 file systems were not
tested at this time.

@@

In the following test, a single Ceph host drives $n$ OSDs, where $n$
increases from one to eleven. The result is illustrated in Figure~\ref{fig:osd-scale}.
We ran the test against a single client with four concurrent processes. In this test
case, we observe that the OSS exhibits near linear scalability up to nine
OSDs, and is still trending upwards at eleven OSDs. This suggests that we have not reached the
saturation point yet. Additional testing would require provisioning more OSDs on the SFA10K backend.

@@

In this test, we exercise OSS numbers from one to four, driven by four clients with four
concurrent process for each client. Each additional OSS adds eleven more OSDs into
play. We observe that Ceph exhibits linear scaling with regard to
number of servers as well, at least in the given set of servers. However, the peak
performance we are seeing is about the half of what are expecting from the SFA10K.
For writes, it is attributed to the way Ceph performs
journaling: Ceph does not support meta-data only journaling, therefore every
write is the equivalent of a double-write: once to the data device, once to the
journaling device. This effectively cuts the system bandwidth in half. That said,
it does not explain the read performance -- it is better than write, but 
still far from the theoretical maximum.

@@

We used the synthetic IOR benchmark suite the for file system level test. The particular
parameter setup is show in Table \ref{tbl:ior}. Each client node has 6 GB of
physical memory, the block size is set so as to mitigate cache effects. In
addition, the test harness program will issue the following commands at the
beginning of each test:

@@

Our first round of tests was less than ideal as we encountered various issues. For
the sake of completeness, we first summarize the results, then discuss
further tuning efforts and improvements.

The full permutation of IOR parameters were not explored due to IO errors we encountered.
We were, however, able to record results in two extreme cases as far as
transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
(4) and same block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

@@

\begin{itemize}
  \item The small read performance is almost an anomaly -- we need to
  investigate why it is so low compare to write performance.
  \item The large read performance is almost half of the write performance,
  which is the opposite of the RADOS-level results. 
  \item The write performance is half of what we can obtain from
  RADOS Bench. When number of clients reaches 8, there is a significant
  performance drop as well. 
\end{itemize}

@@

As a result of this testing, performance was again improved slightly by
increasing the size of various Ceph buffers and queues, enabling AIO journals,
and increasing the number of OSD op threads.

\subsection{Disable Cache Mirroring on controllers}

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  A significant amount of time was spent
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The 2nd RAID processor on each DDN controller would max out when
3 or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.

@@

With cache mirroring disabled, write performance when using all four servers
improved dramatically, as illustrated in
Figure~\ref{fig:rados-ddn-mirror-disabled}. With BTRFS, for example, we hit over
5.5 GB/s from the clients.  When accounting for journal writes, that is over
11 GB/s to the disks and very close to what the DDN chassis is capable of doing. 
Unfortunately, read performance did not scale as well.

@@

During these tests, a trend that previously had been seen became more apparent.
During reads, there were periods of high performance followed by periods of low
performance or outright stalls that could last for up to 20 seconds at a time. 
After several hours of diagnostics, Inktank observed that outstanding operations
on the clients were not being shown as outstanding on the OSDs.  This appeared
to be very similar to a problem Jim Schutt at Sandia National labs encountered
with TCP autotuning in the Linux Kernel.
\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}.
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this will make a notable improvement
on Ceph read performance, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

@@

We now repeated the previous RADOS scaling tests with these improvements in place.
The first test was done on a single node with RADOS Bench to see how close the
underlying object store could get to the node hardware limitations as the number
of OSDs/LUNs used on the node increased. Note all the tests performed were against
XFS-formatted storage.

@@

We also repeated tests looking at RADOS Bench performance as the
number of OSD server nodes increases. The results are summarized in
Figure~\ref{fig:rados-064-oss}. As the number of nodes increases, performance
scales nearly linearly for both reads and writes.

@@

The initial stability issues we encountered are fixed by moving 
from Ceph version 0.48/0.55 to 0.64, the latest stable version at the time. Now IOR test could
complete even during long runs. This is another sign of how much Ceph
development is in flux.

Another fix comes in the way we create the pool: the default data pool being used
by previous CephFS cluster are set to 2x replication, which can potentially
halve the write performance. Even with these changes in place, Inktank still
reproduced the less-than-ideal write performance and very poor read
performance as observed by ORNL.  Further, by increasing the number of IOR
processes per client node, read performance actually degraded further
indicating some kind of contention either on the clients or on the OSD
servers.

@@

ORNL at this point was able to both make more client nodes available and also
install a profiling tool called \verb!perf! that is extremely useful for
profiling both kernel and user space code.  Profiling with \verb!perf! showed
high CPU utilization on the client due to crc32c processing in the Ceph kernel
client.  Luckily, crc32 checksums can be disabled by changing the CephFS mount
options:

@@

We observed that IOR write throughput increased dramatically and is now very
close to the throughput we were able to achieve with RADOS Bench, but reads
continued to be slow and continued to scale inversely with the number of client
processes.  Please note that since these tests were performed, Inktank has
implemented SSE4-based CRC32 code for Intel CPUs.  While any kernel based CRC32
processing should have already been using SSE4 instructions on Intel CPUs, this
will allow any user-land Ceph processes to process CRC32 checksums with
significantly less overhead.

@@

ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
RADOS Bench test to verify that there was no degradation vs previous tests.  The
results were extremely positive.

@@

With the kernel changes writes performance improved slightly, while read
performance improved dramatically.  In addition to the kernel change, Sage Weil
suggested increasing the amount of read-ahead being performed by the CephFS
kernel client:

@@

By installing a new kernel, increasing read-ahead, and increasing the number of
client IOR processes, we were able to achieve a very satisfactory result on this
test run.

@@

As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we are
seeing a much improved picture of read and write performance, very much in
line with RADOS bench performance.

@@

We observe a couple of places where the average write throughput is quite a
bit lower than the maximum.  This behavior was observed during other tests as well,
indicating that we may have periods of time where write throughput is
temporarily degrading.  Despite these issues, performance generally seems to be
improving as the number of clients increases.  Writes seem to be topping out at
around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
would continue scaling with more clients and get closer to the 8 GB/s+ numbers we
saw with RADOS Bench.

@@

  \item Ceph is built on the assumption that the underlying hardware components
  are unreliable, with little or no redundancy and failure detection capability.
  This is not the case in leadership computing facilities. We have disabled
  replication for pools, but this will take a toll somewhere in the processing
  and we do not know if this is significant.

  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
  system that has locally attached disk. However, this presents a problem in DDN
  SFA10-like hardware, where the backend LUNs are exposed as block device
  through SRP over IB. The journaling write would requires double bandwidth
  compare to Lustre-like metadata only journaling mechanism. For Ceph to anything
  viable in this facility, there has to be a solution for this.

  \item Ceph is observed to have consistent results and linear scalability at the
  RADOS level. However, it broke down at the file system level with synthetic
  benchmark suites such as IOR. We have experienced large performance swings
  during different runs, very low read performance when transfer size is small,
  and IO errors tend to happen when system is under stress (more clients and
  large transfer sizes). These are not particularly reproducible results, but it
  suggests the level of maturity still have a long way to go.

@@

This crush map is just an example of full OSD mapping. As we create and
re-create different testbed subests with different OSD configurations, the map will
change accordingly.
